\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Huge \href{https://www.payamyek.com/}{Payam Yektamaram}}} & 307-778 Sheppard Ave West, Toronto, ON\\
  \href{https://ca.linkedin.com/in/payamyek}{\faIcon{linkedin} linkedin.com/in/payamyek}  &  \href{mailto:payam.yektamaram@mail.utoronto.ca}{payam.yektamaram@mail.utoronto.ca}\\
  \href{https://github.com/payamyek}{\faIcon{github} github.com/payamyek} & (647)-867-5038
\end{tabular*}

\bigbreak

Systems Developer Hiring Manager   \hfill       Friday August 19, 2022 \\
Municipal Property Assessment Corporation  \\
1340 Pickering Pkwy,  \\  
Pickering, ON L1C 3C0 \\

\bigbreak

Dear Systems Developer Hiring Manager,

% INTRO PARAGRAPH
\bigbreak 
\noindent I am extremely interested in the Systems Developer (ITA3) position at the Municipal Property Assessment Corporation (MPAC) which was posted on the Brain Hunter job portal. As a Computer Science graduate from the University of Toronto, I want to be part of an organization recognized as one of Greater Toronto’s Top Employers for 2022 due to its amazing support of its employees and conducive learning environment. I am confident that my one year of experience as a Junior Co-op Systems Developer at MPAC makes me a prime candidate for this role due to my experiences in developing RESTful APIs, web development, and excellent communication skills.

% TECHNICAL SKILLS
\bigbreak
\noindent As a previous systems developer at MPAC, I have garnered expertise in developing robust RESTful APIs. As I co-developed the \textit{Lookup Service} using Python by strictly following REST principles by ensuring that all operations were centred around the abstract models of resources and entities. This ensured the API was intuitive for clients to use as it followed pre-existing standards followed by the industry. The \textit{Lookup Service} also took advantage of the asynchronous nature of Python and thus was built in a way that effectively utilized computer resources to reduce latency time. I was also exposed to web development as I co-developed a frontend interface for the \textit{Lookup Service} using React to create a seamless experience for users. The frontend utilized popular frontend libraries like Bootstrap that helped to construct an intuitive user experience. The skills and knowledge I have gained ensure that I can succeed in developing and maintaining RESTful APIs and web applications due to my expertise in system development.

% INTERPERSONAL EXPERIENCES
\bigbreak
\noindent

As a previous systems developer at MPAC, I have developed robust communication skills by working in an Agile team. I have participated in many sprint planning sessions where I was able to clearly and effectively communicate my expertise, knowledge, and concerns with the team to ensure our sprints were successful. I always approached team meetings with respect, clarity and conciseness to ensure that the meetings stayed on track and that the team could effectively understand my ideas. I have also delivered an application demonstration to the I.T director, communicating the purpose, intentions, and utility of the \textit{Lookup Service} which was well received by all participants. These experiences will allow me to work cohesively in a team environment as I can make sure my opinions and concerns are heard while fostering a professional and productive work environment.

% CONCLUSION 
\bigbreak
\noindent I ensure that my vast experiences in RESTful APIs, web development and excellent communication skills make me a prime candidate for the Systems Developer position at the Municipal Property Assessment Corporation. I appreciate your consideration and am eager to meet with you to further discuss my application. Thank you. 

% SIGN OFF
\bigbreak

Kind Regards, \\ \vspace{10pt}
Payam Yektamaram

\end{document}