\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Huge \href{https://www.payamyek.com/}{Payam Yektamaram}}} & Toronto, ON\\
  \href{https://ca.linkedin.com/in/payamyek}{\faIcon{linkedin} linkedin.com/in/payamyek}  &  \href{payamyek@gmail.com}{payamyek@gmail.com}\\
  \href{https://github.com/payamyek}{\faIcon{github} github.com/payamyek} & (647)-867-5038
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto Scarborough}{Toronto, ON}
      {Honours Bachelors of Science in Computer Science;  GPA: 3.89/4.00}{Sept. 2018 -- Aug. 2022}
 \resumeSubHeadingListEnd

 %-------- SKILLS ------------
\section{Skills}
 \resumeSubHeadingListStart
 	\resumeSubItem{Languages}{Python, Java, C, JavaScript, TypeScript, SQL, Groovy, Haskell, Assembly}
 	\resumeSubItem{Web Technologies}{React, React Native, Vue, Expo, CSS, SASS, SCSS, HTML, Bootstrap}
 	\resumeSubItem{Database Technologies}{MongoDB, PostgreSQL, DocumentDB, Neo4J}
 	\resumeSubItem{Cloud Technologies}{Amazon Web Services, DigitalOcean, Docker, Auth0, Rancher Kubernetes Management}
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
   \resumeSubheading
      {Municipal Property Assessment Corporation}{Pickering, ON}
      {Systems Developer}{Sep. 2022 - Present}
      \resumeItemListStart
        \item{ \small{Proactively protected crucial MPAC systems from potential library based vulnerabilities by continuously monitoring and updating project dependencies resulting in the 100\% removal of high risk system breaches }}
       \resumeItemListEnd
  
    \resumeSubheading
      {Municipal Property Assessment Corporation}{Pickering, ON}
      {Junior Co-op Systems Developer}{Jan. 2020 - Dec. 2020}
      \resumeItemListStart
        \item{ \small{Abolished inconsistency of business data for MPAC micro-services by developing a Python RESTful micro-service known as the \textit{Lookup Service} which reduced data inconsistency by 100\% for three vital MPAC services}}
        \item{ \small{Demolished the need for Business Analysts to concern system developers when business data required updates by creating a React frontend interface for the \textit{Lookup Service} saving developers and analysts hours of time}}
        \item{\small{Prevented 99\% of application bugs for the \textit{Lookup Service} by developing a robust unit testing suite containing over 300 test cases covering 93\% of the codebase which drastically expedited the development process}}
        \item{\small{Restricted unauthorized and unauthenticated users from accessing the \textit{Lookup Service} by securing the application through JSON Web Tokens ensuring MPAC business data was properly safeguarded from exploitation}}
        \item{\small{Brought a vision for the new MPAC Insight workflow to life by developing dashboard module prototypes using React that was powered by Ontario housing data which was well received by the team leads}}
       \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  	\resumeSubItem{\href{https://github.com/UTSCC09/project-frontend-frauds}{Air Toronto \faIcon{github}}}{Comprehensive flight ticket booking system built using Vue3 utilizing asynchronous task queues with workers to process application webhooks and emails.}
  	\resumeSubItem{Pawsup}{Mobile application that enabled clients to purchase pet services built with React Native through Expo to deliver mobile app for both Android and iOS environments.}
    \resumeSubItem{\href{https://github.com/payamyek/Jeopardy}{Jeopardy \faIcon{github}}}
      {Game of Jeopardy that allowed two teams to play a full fledged game with live score tracking that was built using React and Redux for state management.}
     \resumeSubItem{\href{https://github.com/payamyek/portfolio-site}{Portfolio \faIcon{github}}}
      {Personal portfolio site made using React.js utilizing TailWind CSS deployed on Vercel.}
    \resumeSubItem{\href{https://github.com/payamyek/SupremeCarRentals}{Supreme Car Rentals \faIcon{github}}}
      {Car rental application built using Java Swing powered by an embedded SQLite database which allowed clients to rent cars and receive an auto-generated printable PDF invoice with booking details.}
      
  \resumeSubHeadingListEnd

 
 %--------CERTIFICATES------------
\section{Certificates}
 \resumeSubHeadingListStart
   \item{\small{\textbf{Focus on Information Technology (FIT)}{ – Software Design and Development}} \hfill \textit{\small{Jun. 2018}}}
   \item{\small{\vspace{-6pt} \textbf{Focus on Information Technology (FIT)}{ – Network Systems and Operations}} \hfill \textit{\small{Jun. 2018}} }
   \item{\small{\vspace{-6pt} \textbf{Cisco}{ – IT Essentials}} \hfill \textit{\small{Jun. 2018}}}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}